Metrics

### 2023-12-10 src/plots.Rmd
Add plot for cases by age and sex

Clean `age_range` labels to include only values and unit of measure.

```{r}
df <- raw_df %>% mutate(
    "age_range" = str_replace(
        age_range,
        "\\s*\\(.*\\)",
        ""
    ))
df
```

@@

#### Cases by Sex

#### Cases by Age Group

@@

# Prepare boxplot data
alldata <- out %>%
    select(
        Model,
        `PCCC`,
        `PCCC Agreement`,
        `CSMF Accuracy`,
        `CSMF Accuracy Agreement`
    ) %>%
    rename(
         All = `PCCC`,
         Agreed = `PCCC Agreement`
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -c(
            Model,
            `CSMF Accuracy`,
            `CSMF Accuracy Agreement`
        ),
        names_to = "Stage",
        values_to = "PCCC"
    ) %>%
    group_by(Stage) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(
            PCCC <= min(PCCC) * 1.05,
            paste0(Model, "\n(", round(PCCC, 2), ", CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
            NA
        ),
        "PCCC Max" = if_else(
            PCCC >= max(PCCC) * 0.97,
            paste0(Model, "\n(", round(PCCC, 2), ", CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
            NA
        ),
        "PCCC Mid" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            paste0(Model, "\n(", round(PCCC, 2), ", CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
            NA
        ),
        "PCCC Mid Value" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            PCCC,
            NA
        ),
        "PCCC Min" = if_else( # Combine into one row if close PCCC
            `PCCC` == min(PCCC),
            if_else(
                sum(!is.na(`PCCC Min`)) > 1,
                paste0(na.omit(`PCCC Min`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\,\\s*", "\n("),
                    collapse = "\n"
                )
            ),
            NA
        ),
        "PCCC Max" = if_else(
            `PCCC` == max(PCCC),
            if_else(
                sum(!is.na(`PCCC Max`)) > 1,
                paste0(na.omit(`PCCC Max`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\,\\s*", "\n("),
                    collapse = "\n"
                )
            ),
            NA
        )
    ) %>%
    mutate( # re-order stage
        Stage = factor(Stage, levels = c(
            "Agreed",
            "All"
        ))
    ) %>%
    mutate( # rename stages with counts
        Stage = recode(Stage, !!!stage_remap)
    )

@@

# Prepare boxplot data
agedata <- out %>%
    select(
        Model,
        `PCCC Adult Agreement`,
        `PCCC Child Agreement`,
        `PCCC Neo Agreement`,
        `CSMF Accuracy Adult Agreement`,
        `CSMF Accuracy Child Agreement`,
        `CSMF Accuracy Neo Agreement`
    ) %>%
    rename(
         Adult = `PCCC Adult Agreement`,
         Child = `PCCC Child Agreement`,
         Neonatal = `PCCC Neo Agreement`
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -c(
            Model,
            `CSMF Accuracy Adult Agreement`,
            `CSMF Accuracy Child Agreement`,
            `CSMF Accuracy Neo Agreement`
        ),
        names_to = "Age Group",
        values_to = "PCCC"
    ) %>%
    group_by(`Age Group`) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(
            PCCC <= min(PCCC) * 1.15,
            paste0(
                Model, "\n(",
                if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
                "CSMF=", round(case_when(
                    `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
                    `Age Group` == "Child"  ~ `CSMF Accuracy Child Agreement`,
                    `Age Group` == "Neonatal"  ~ `CSMF Accuracy Neo Agreement`
                ),2), ")"),
            NA
        ),
        "PCCC Max" = if_else(
            PCCC >= max(PCCC) * 0.95,
            paste0(
                Model, "\n(",
                if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
                ", CSMF=", round(case_when(
                    `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
                    `Age Group` == "Child"  ~ `CSMF Accuracy Child Agreement`,
                    `Age Group` == "Neonatal"  ~ `CSMF Accuracy Neo Agreement`
                ),2), ")"),
            NA
        ),
        "PCCC Mid" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            paste0(
                Model, "\n(", round(PCCC, 2),
                ", CSMF=", round(case_when(
                    `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
                    `Age Group` == "Child"  ~ `CSMF Accuracy Child Agreement`,
                    `Age Group` == "Neonatal"  ~ `CSMF Accuracy Neo Agreement`
                ),2), ")"),
            NA
        ),
        "PCCC Mid Value" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            PCCC,
            NA
        ),
        "PCCC Min" = if_else( # Combine into one row if close PCCC
            `PCCC` == min(PCCC),
            if_else(
                sum(!is.na(`PCCC Min`)) > 1,
                paste0(na.omit(`PCCC Min`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\,\\s*", "\n("),
                    collapse = "\n"
                )
            ),
            NA
        ),
        "PCCC Max" = if_else(
            `PCCC` == max(PCCC),
            if_else(
                sum(!is.na(`PCCC Max`)) > 1,
                paste0(na.omit(`PCCC Max`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\,\\s*", "\n("),
                    collapse = "\n"
                )
            ),
            NA
        )
    )%>%
    mutate( # re-order age
        "Age Group" = factor(`Age Group`, levels = c(
            "Neonatal",
            "Child",
            "Adult"
        ))
    ) %>%
    mutate( # rename ages with counts
        "Age Group" = recode(`Age Group`, !!!age_remap)
    )

# Plot boxplot
ageplot <- agedata %>%
    ggplot(aes(x = `Age Group`, y = PCCC)) +
    geom_boxplot(
        linewidth = 0.5,
        width = 0.25
    ) +
    geom_point(
        aes(y = `PCCC Mid Value`),
        shape = 1,
        size = 1.5,
        fill = "white",
        color = "darkgray",
        alpha = 0.8,
        position = position_nudge(x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Min`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.055)
    ) +
    geom_text(
        aes(label = `PCCC Max`),
        color = "#4d4d4d",
        size = 2,
        hjust = 0,
        position = position_nudge(y = 0.055)
    ) +
    geom_text(
        aes(label = `PCCC Mid`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.015, x = -0.3)
    ) +
    stat_summary( # min pccc txt on boxplot
        geom = "text",
        fun = min,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = -0.025),
        size = 3
    ) +
    stat_summary( # max pccc txt on boxplot
        geom = "text",
        fun = max,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = 0.025),
        size = 3
    ) +
    labs(
        x = paste0("Physician Agreed Records (n=", nagree, ", 100%)"),
        y = "PCCC (0=Low, 1=High)"
    ) +
    ylim(0.25, 0.85) +
    coord_flip() +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        plot.margin = margin(t = 16, b = 12, l = 12, r = 12),
        axis.line = element_line(color = "black"),
        axis.title.x = element_text(margin = margin(t = 10)),
        axis.title.y = element_text(margin = margin(r = 10)),
        axis.line.x = element_line(
            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
        ),
        axis.line.y = element_blank()
    )

@@

    # Calculate num and perc cases for age range
    narange <- df %>% filter(age_range == ar & is_agreed == TRUE) %>% nrow
    parange <- (narange / nagree) * 100
    parange_label <- if (round(parange) >= 1) round(parange) else "<1"

    # Break age range into newlines if more than 3 words
    if (str_count(ar, "\\s+") > 3) {
        arange_label <- str_replace(ar, "(\\S+\\s+\\S+\\s+\\S+) ", "\\1\n")
    } else {
        arange_label <- ar
    }

    # Add label for age ranges
    arange_remap[[ar]] <- paste0(arange_label, "\n(n=", narange, ", ", parange_label, "%)")

@@

# Prepare boxplot data
ardata <- out %>%
    select(
        Model,
        starts_with("PCCC Age Agree ")
    ) %>%
    rename_at(
         vars(-Model),
         ~gsub("PCCC Age Agree ", "", .)
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -Model,
        names_to = "Age Range",
        values_to = "PCCC"
    ) %>%
    mutate( # rename cod with counts
        "Age Range" = recode(`Age Range`, !!!arange_remap)
    ) %>%
    group_by(`Age Range`) %>%
    mutate( # Make values less than 0 equal to 0
        PCCC = if_else(PCCC <= 0, 0, PCCC)
    ) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(
            PCCC <= min(PCCC) * 1.03,
            paste0(
                Model,
                if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
            ),
            NA
        ),
        "PCCC Max" = if_else(
            PCCC >= max(PCCC) * 0.97,
            paste0(
                Model,
                if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
            ),
            NA
        ),
        "PCCC Mid" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            paste0(Model, "\n(", round(PCCC, 2), ")"),
            NA
        ),
        "PCCC Min" = if_else( # Combine into one row if close PCCC
            `PCCC` == min(PCCC),
            if_else(
                sum(!is.na(`PCCC Min`)) > 1,
                paste0(na.omit(`PCCC Min`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
                    collapse = "\n"
                )
            ),
            NA
        ),
        "PCCC Max" = if_else(
            `PCCC` == max(PCCC),
            if_else(
                sum(!is.na(`PCCC Max`)) > 1,
                paste0(na.omit(`PCCC Max`), collapse = "\n"),
                paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
                       collapse = "\n")
            ),
            NA
        )
    )

@@

# Prepare boxplot data
coddata <- out %>%
    select(
        Model,
        starts_with("PCCC COD Agree ")
    ) %>%
    rename_at(
         vars(-Model),
         ~gsub("PCCC COD Agree ", "", .)
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -Model,
        names_to = "COD",
        values_to = "PCCC"
    ) %>%
    mutate( # rename cod with counts
        "COD" = recode(`COD`, !!!cod_remap)
    ) %>%
    group_by(`COD`) %>%
    mutate( # Make values less than 0 equal to 0
        PCCC = if_else(PCCC <= 0, 0, PCCC)
    ) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(
            PCCC <= min(PCCC) * 1.03,
            paste0(
                Model,
                if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
            ),
            NA
        ),
        "PCCC Max" = if_else(
            PCCC >= max(PCCC) * 0.97,
            paste0(
                Model,
                if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
            ),
            NA
        ),
        "PCCC Mid" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            paste0(Model, "\n(", round(PCCC, 2), ")"),
            NA
        ),
        "PCCC Min" = if_else( # Combine into one row if close PCCC
            `PCCC` == min(PCCC),
            if_else(
                sum(!is.na(`PCCC Min`)) > 1,
                paste0(na.omit(`PCCC Min`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
                    collapse = "\n"
                )
            ),
            NA
        ),
        "PCCC Max" = if_else(
            `PCCC` == max(PCCC),
            if_else(
                sum(!is.na(`PCCC Max`)) > 1,
                paste0(na.omit(`PCCC Max`), collapse = "\n"),
                paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
                       collapse = "\n")
            ),
            NA
        )
    )

>>>>

Clean `age_range` labels to include only values and unit of measure in titlecase.

```{r}
df <- raw_df %>% mutate(
    "age_range" = str_to_title(str_replace(
        age_range,
        "\\s*\\(.*\\)",
        ""
    )),
    "age_range" = if_else(
        !str_detect(age_range, "Year|Years|Day|Days|month|Months|week|Weeks"),
        paste0(age_range, " Years"),
        age_range
    )
)
df
```

@@

# Num and perc of agreed cases
nall <- nrow(df)
nagree <- nrow(df %>% filter(is_agreed == TRUE))
pagree <- (nagree / nall) * 100

# Create labels to axis titles
y_title <- paste0("Physician Agreed Records (n=", nagree, ", 100%)")

```

#### Cases by Age Group and Sex

Display a plot of cases by age group separated by sex.

# Calc age and sex counts
nadult <- nrow(df %>% filter(age == "adult" & is_agreed == TRUE))
nchild <- nrow(df %>% filter(age == "child" & is_agreed == TRUE))
nneo <- nrow(df %>% filter(age == "neo" & is_agreed == TRUE))

# Calc age and sex perc
padult <- (nadult / nagree) * 100
pchild <- (nchild / nagree) * 100
pneo <- (nneo / nagree) * 100

# Create age with counts
age_remap <- c(
    "Adult" = paste0("Adult, 12+ years\n(n=", nadult, ", ", round(padult), "%)"),
    "Child" = paste0("Child, 28 days to 11 years\n(n=", nchild, ", ", round(pchild), "%)"),
    "Neo" = paste0("Neonatal, <28 days\n(n=", nneo, ", ", round(pneo), "%)")
)

# Get counts for ages

# Format the data for plotting
asdata <- df %>%
    filter(is_agreed == TRUE) %>%
    group_by(age, sex) %>%
    summarize(count = n()) %>%
    mutate(
        age = str_to_title(age),
        sex = paste0(
            sex, " (n=", count, ", ",
            round(count / case_when(
                age == "Adult" ~ nadult,
                age == "Child" ~ nchild,
                age == "Neo" ~ nneo
            ) * 100), "%)"
        )
    ) %>%
    mutate( # re-order age
        age = factor(age, levels = c(
            "Adult",
            "Child",
            "Neo"
        ))
    ) %>%
    mutate( # rename ages with counts
        age = recode(age, !!!age_remap)
    )

# Plot the data
asplot <- asdata %>%
    ggplot(aes(x = factor(age), y = count, fill = sex)) +
    geom_bar(
        stat = "identity",
        fill = "white",
        color = "black"
    ) +
    geom_text(
        aes(label = sex),
        position = position_stack(vjust = 0.5),
        size = 2.5,
        color = "black"
    ) +
    labs(
        y = y_title,
        x = element_blank(),
        fill = "Sex"
    ) +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        axis.title.x = element_text(margin = margin(t = 10)),
        axis.title.y = element_text(margin = margin(r = 10))
    )

# Save the plot
asplot
ggsave("../manuscript/fig-data-agegroup.pdf", plot = asplot, dpi = 300)
```

@@

# Prepare boxplot data
alldata <- out %>%
    select(
        Model,
        `PCCC`,
        `PCCC Agreement`,
        `CSMF Accuracy`,
        `CSMF Accuracy Agreement`
    ) %>%
    rename(
         All = `PCCC`,
         Agreed = `PCCC Agreement`
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -c(
            Model,
            `CSMF Accuracy`,
            `CSMF Accuracy Agreement`
        ),
        names_to = "Stage",
        values_to = "PCCC"
    ) %>%
    group_by(Stage) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(
            PCCC <= min(PCCC) + 0.05,
            paste0(
                Model, "\n(",
                if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
                "CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
            NA
        ),
        "PCCC Max" = if_else(
            PCCC >= max(PCCC) - 0.05,
            paste0(
                Model, "\n(",
                if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
                "CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
            NA
        ),
        "PCCC Mid" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            paste0(Model, "\n(", round(PCCC, 2), ", CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
            NA
        ),
        "PCCC Mid Value" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            PCCC,
            NA
        ),
        "PCCC Min" = if_else( # Combine into one row if close PCCC
            `PCCC` == min(PCCC),
            if_else(
                sum(!is.na(`PCCC Min`)) > 1,
                paste0(na.omit(`PCCC Min`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\,\\s*", "\n("),
                    collapse = "\n"
                )
            ),
            NA
        ),
        "PCCC Max" = if_else(
            `PCCC` == max(PCCC),
            if_else(
                sum(!is.na(`PCCC Max`)) > 1,
                paste0(na.omit(`PCCC Max`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\,\\s*", "\n("),
                    collapse = "\n"
                )
            ),
            NA
        )
    ) %>%
    mutate( # re-order stage
        Stage = factor(Stage, levels = c(
            "Agreed",
            "All"
        ))
    ) %>%
    mutate( # rename stages with counts
        Stage = recode(Stage, !!!stage_remap)
    )

@@

# Prepare boxplot data
agedata <- out %>%
    select(
        Model,
        `PCCC Adult Agreement`,
        `PCCC Child Agreement`,
        `PCCC Neo Agreement`,
        `CSMF Accuracy Adult Agreement`,
        `CSMF Accuracy Child Agreement`,
        `CSMF Accuracy Neo Agreement`
    ) %>%
    rename(
         Adult = `PCCC Adult Agreement`,
         Child = `PCCC Child Agreement`,
         Neonatal = `PCCC Neo Agreement`
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -c(
            Model,
            `CSMF Accuracy Adult Agreement`,
            `CSMF Accuracy Child Agreement`,
            `CSMF Accuracy Neo Agreement`
        ),
        names_to = "Age Group",
        values_to = "PCCC"
    ) %>%
    group_by(`Age Group`) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(
            PCCC <= min(PCCC) + 0.05,
            paste0(
                Model, "\n(",
                if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
                "CSMF=", round(case_when(
                    `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
                    `Age Group` == "Child"  ~ `CSMF Accuracy Child Agreement`,
                    `Age Group` == "Neonatal"  ~ `CSMF Accuracy Neo Agreement`
                ),2), ")"),
            NA
        ),
        "PCCC Max" = if_else(
            PCCC >= max(PCCC) - 0.05,
            paste0(
                Model, "\n(",
                if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
                "CSMF=", round(case_when(
                    `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
                    `Age Group` == "Child"  ~ `CSMF Accuracy Child Agreement`,
                    `Age Group` == "Neonatal"  ~ `CSMF Accuracy Neo Agreement`
                ),2), ")"),
            NA
        ),
        "PCCC Mid" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            paste0(
                Model, "\n(", round(PCCC, 2),
                ", CSMF=", round(case_when(
                    `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
                    `Age Group` == "Child"  ~ `CSMF Accuracy Child Agreement`,
                    `Age Group` == "Neonatal"  ~ `CSMF Accuracy Neo Agreement`
                ),2), ")"),
            NA
        ),
        "PCCC Mid Value" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            PCCC,
            NA
        ),
        "PCCC Min" = if_else( # Combine into one row if close PCCC
            `PCCC` == min(PCCC),
            if_else(
                sum(!is.na(`PCCC Min`)) > 1,
                paste0(na.omit(`PCCC Min`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\,\\s*", "\n("),
                    collapse = "\n"
                )
            ),
            NA
        ),
        "PCCC Max" = if_else(
            `PCCC` == max(PCCC),
            if_else(
                sum(!is.na(`PCCC Max`)) > 1,
                paste0(na.omit(`PCCC Max`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\,\\s*", "\n("),
                    collapse = "\n"
                )
            ),
            NA
        )
    ) %>%
    mutate( # re-order age
        "Age Group" = factor(`Age Group`, levels = c(
            "Neonatal",
            "Child",
            "Adult"
        ))
    ) %>%
    mutate( # rename ages with counts
        "Age Group" = recode(`Age Group`, !!!age_remap)
    )

# Plot boxplot
ageplot <- agedata %>%
    ggplot(aes(x = `Age Group`, y = PCCC)) +
    geom_boxplot(
        linewidth = 0.5,
        width = 0.25
    ) +
    geom_point(
        aes(y = `PCCC Mid Value`),
        shape = 1,
        size = 1.5,
        fill = "white",
        color = "darkgray",
        alpha = 0.8,
        position = position_nudge(x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Min`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.055)
    ) +
    geom_text(
        aes(label = `PCCC Max`),
        color = "#4d4d4d",
        size = 2,
        hjust = 0,
        position = position_nudge(y = 0.055)
    ) +
    geom_text(
        aes(label = `PCCC Mid`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.015, x = -0.3)
    ) +
    stat_summary( # min pccc txt on boxplot
        geom = "text",
        fun = min,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = -0.025),
        size = 3
    ) +
    stat_summary( # max pccc txt on boxplot
        geom = "text",
        fun = max,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = 0.025),
        size = 3
    ) +
    labs(
        x = paste0("Physician Agreed Records (n=", nagree, ", 100%)"),
        y = "PCCC (0=Low, 1=High)"
    ) +
    ylim(0.25, 0.9) +
    coord_flip() +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        plot.margin = margin(t = 16, b = 12, l = 12, r = 12),
        axis.line = element_line(color = "black"),
        axis.title.x = element_text(margin = margin(t = 10)),
        axis.title.y = element_text(margin = margin(r = 10)),
        axis.line.x = element_line(
            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
        ),
        axis.line.y = element_blank()
    )

@@

    # Calc num and perc cases for age range
    narange <- df %>% filter(age_range == ar & is_agreed == TRUE) %>% nrow
    parange <- (narange / nagree) * 100
    parange_label <- if (round(parange) >= 1) round(parange) else "<1"

    # Add label for age ranges
    arange_remap[[ar]] <- paste0(
        ar,
        "\n(n=", narange, ", ", parange_label, "%)"
    )

@@

# Prepare boxplot data
ardata <- out %>%
    select(
        Model,
        starts_with("PCCC Age Agree ")
    ) %>%
    rename_at(
         vars(-Model),
         ~gsub("PCCC Age Agree ", "", .)
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -Model,
        names_to = "Age Range",
        values_to = "PCCC"
    ) %>%
    mutate( # rename cod with counts
        "Age Range" = recode(`Age Range`, !!!arange_remap)
    ) %>%
    group_by(`Age Range`) %>%
    mutate( # Make values less than 0 equal to 0
        PCCC = if_else(PCCC <= 0, 0, PCCC)
    ) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(
            PCCC <= min(PCCC) + 0.05,
            paste0(
                Model,
                if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
            ),
            NA
        ),
        "PCCC Max" = if_else(
            PCCC >= max(PCCC) - 0.05,
            paste0(
                Model,
                if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
            ),
            NA
        ),
        "PCCC Mid" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            paste0(Model, "\n(", round(PCCC, 2), ")"),
            NA
        ),
        "PCCC Min" = if_else( # Combine into one row if close PCCC
            `PCCC` == min(PCCC),
            if_else(
                sum(!is.na(`PCCC Min`)) > 1,
                paste0(na.omit(`PCCC Min`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
                    collapse = "\n"
                )
            ),
            NA
        ),
        "PCCC Max" = if_else(
            `PCCC` == max(PCCC),
            if_else(
                sum(!is.na(`PCCC Max`)) > 1,
                paste0(na.omit(`PCCC Max`), collapse = "\n"),
                paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
                       collapse = "\n")
            ),
            NA
        )
    )

@@

# Prepare boxplot data
coddata <- out %>%
    select(
        Model,
        starts_with("PCCC COD Agree ")
    ) %>%
    rename_at(
         vars(-Model),
         ~gsub("PCCC COD Agree ", "", .)
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -Model,
        names_to = "COD",
        values_to = "PCCC"
    ) %>%
    mutate( # rename cod with counts
        "COD" = recode(`COD`, !!!cod_remap)
    ) %>%
    group_by(`COD`) %>%
    mutate( # Make values less than 0 equal to 0
        PCCC = if_else(PCCC <= 0, 0, PCCC)
    ) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(
            PCCC <= min(PCCC) + 0.05,
            paste0(
                Model,
                if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
            ),
            NA
        ),
        "PCCC Max" = if_else(
            PCCC >= max(PCCC) - 0.05,
            paste0(
                Model,
                if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
            ),
            NA
        ),
        "PCCC Mid" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            paste0(Model, "\n(", round(PCCC, 2), ")"),
            NA
        ),
        "PCCC Min" = if_else( # Combine into one row if close PCCC
            `PCCC` == min(PCCC),
            if_else(
                sum(!is.na(`PCCC Min`)) > 1,
                paste0(na.omit(`PCCC Min`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
                    collapse = "\n"
                )
            ),
            NA
        ),
        "PCCC Max" = if_else(
            `PCCC` == max(PCCC),
            if_else(
                sum(!is.na(`PCCC Max`)) > 1,
                paste0(na.omit(`PCCC Max`), collapse = "\n"),
                paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
                       collapse = "\n")
            ),
            NA
        )
    )
